---
title: "gie R Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## gie

gie is an R package for wrapping the Gas Infrastructure Europe (GIE) REST API.

## API Key

The official documentation from GIE can be found [here](https://agsi.gie.eu/GIE_API_documentation_v003.pdf)

Before proceeding with the examples you need to get a token / API key from the [GIE homepage](https://agsi.gie.eu/#/api). On the API page you can lookup EIC codes for the companies and facilities.

## EIC Codes

You can find the EIC codes here:

- Gas: https://agsi.gie.eu/#/api
- LNG: https://alsi.gie.eu/#/api

## Installation

Simply install from GitHub.

```

remotes::install_github("krose/gie")

```

## Usage

There are four functions. The paramters in the functions are upper-/lower-case sensitive.

The first function gets the aggregated historical data for Europe or Non Europe.

```{r first, message=FALSE, warning=FALSE}

library(tidyverse)
library(gie)

ne_gas <- gie_gas_aggregate("ne")
eu_lng <- gie_lng_aggregate("eu")

glimpse(ne_gas)
glimpse(eu_lng)

```

The second function gets the aggregated historical data for a specific country.

```{r second}

nl <- gie_gas_country("NL")
gb <- gie_lng_country("GB")
glimpse(nl)

```

The third function gets the historical data for a specific company wihtin a country. You can lookup the EIC codes from the API webpage.

```{r third}
eic_gas <- gie_gas_eic("AT", "25X-GSALLC-----E")
eic_lng <- gie_lng_eic("PL", "53XPL000000PLNG6")

glimpse(eic_gas)
glimpse(eic_lng)

```

The last and fourth function gets the historical data for a specific facility from a company wihtin a country. You can lookup the different EIC codes from the API webpage.

```{r fourth}

eic_gas <- gie_gas_company_eic(country_code = "DE",
                       eic_code = "21W000000000100J",
                       eic_company_code = "21X000000001368W")
eic_lng <- gie_lng_company_eic(country_code = "IT",
                       eic_code = "59W0000000000011",
                       eic_company_code = "26X00000117915-0")
glimpse(eic_gas)
glimpse(eic_lng)


```


## Future Development

If needed, params for 'from', 'till' and 'limit' can be implemented.

