---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## gie

gie is an R package for wrapping the Gas Infrastructure Europe (GIE) REST API.

## API Key

The official documentation from GIE can be found [here](https://agsi.gie.eu/GIE_API_documentation_v003.pdf)

Before proceeding with the examples you need to get a token / API key from the [GIE homepage](https://agsi.gie.eu/#/api). On the API page you can lookup EIC codes for the companies and facilities.

## Installation

Simply install from GitHub.

```

remotes::install_github("krose/gie")

```

## Usage

There are four functions. The paramters in the functions are upper-/lower-case sensitive.

The first function gets the aggregated historical data for Europe or Non Europe.

```{r first, message=FALSE, warning=FALSE}

library(tidyverse)
library(gie)

eu <- gie_aggregate("eu")
ne <- gie_aggregate("ne")
glimpse(eu)

```

The second function gets the aggregated historical data for a specific country.

```{r second}

nl <- gie_country("NL")
glimpse(nl)

```

The third function gets the historical data for a specific company wihtin a country. You can lookup the EIC codes from the API webpage.

```{r third}

eic <- gie_eic("PL", "53XPL000000PLNG6")
glimpse(eic)

```

The last and fourth function gets the historical data for a specific facility from a company wihtin a country. You can lookup the different EIC codes from the API webpage.

```{r fourth}

eic <- gie_company_eic(country_code = "DE",
                       eic_code = "21W000000000100J",
                       eic_company_code = "21X000000001368W")
glimpse(eic)

```


## Future Development

If needed, params for 'from', 'till' and 'limit' can be implemented.

